PRCP Preliminary Analysis

### 2020-07-13 analysis/preliminaryAnalysis.Rmd
syncing with latest version

---
title: "Post-replication citation patterns in psychological science: Preliminary analysis"
output: html_document
---

@@

@@

Now we'll plot standardized citation curves and include citations to the set of reference articles (the dashed grey line). In the graphs below, the annual citation counts for both the target article and reference class are standardized against the calendar year with the highest citation count for the target article (i.e., citations received in that year are set at the standardized value of 100). As defined in the protocol, the reference class in each case is all of the articles published in the same year and in the same journal as the target article. For example, for Baumeister et al. (1998), the reference class is all articles published in 1998 in the Journal of Personality and Social Psychology.

@@

Across all cases, `r d_contentAnalysis %>% count(excluded) %>% filter(excluded == T) %>% pull(n)` citing articles had to be excluded because they could not be accessed (n = `r d_contentAnalysis %>% count(exclusionReason) %>% filter(exclusionReason == "No access") %>% pull(n)`), were non-English language (n = `r d_contentAnalysis %>% count(exclusionReason) %>% filter(exclusionReason == "Non-English language") %>% pull(n)`), or because the target article was cited in the references but not in the actual text (n = `r d_contentAnalysis %>% count(exclusionReason) %>% filter(exclusionReason == "Cited in references but not in text") %>% pull(n)`). Excluded articles are represented on the graphs below in light grey.

## Claim correction vs. claim perpetuation

@@

```{r}
rbind(
  d_summary %>%
  filter(case %in% c('baumeister','strack','sripada'),
         pubYear %in% c(2017,2018,2019)),
  d_summary %>%
    filter(case %in% c('carter', 'caruso'),
           pubYear %in% c(2015,2016,2017,2018,2019))
) %>%
  group_by(case) %>%
  summarise(targetCitations = sum(citesTarget,na.rm=T), 
            replicationCitations = sum(citesRep_yes,na.rm=T)) %>%
  mutate(`replicationCitations (%)` = round((replicationCitations/targetCitations)*100,0)) %>%
  kable(caption = 'Citations to replication study by articles citing target study in post-replication years') %>%
  kable_styling(full_width = F)
```

@@

## Principled defense vs. hollow defense

@@

```{r}
rbind(
  d_summary %>%
  filter(case %in% c('baumeister','strack','sripada'),
         pubYear %in% c(2017,2018,2019)),
  d_summary %>%
    filter(case %in% c('carter', 'caruso'),
           pubYear %in% c(2015,2016,2017,2018,2019))
) %>%
  group_by(case) %>%
  summarise(counterargs_yes = sum(counterargs_yes,na.rm=T),
            counterargs_no = sum(counterargs_no,na.rm=T)) %>%
  mutate(
    `Replication cited` = counterargs_yes+counterargs_no,
    counterargs_percent = round(
    (counterargs_yes/(`Replication cited`))*100,
    0)) %>%
  select(case,
         `Replication cited`,
         `Counter arguments used` = counterargs_yes,
         -counterargs_no,
         `Counter arguments used (%)` = counterargs_percent) %>%
  kable(caption = 'Use of counter arguments when target study cited favourably and replication study cited') %>%
  kable_styling(full_width = F)
```

The numbers are quite small here because we are looking only at articles that cited the target study and also cited the replication study favourably (note we actually coded for counter arguments whenever the replication study was cited, but this doesn't increase the counts a great deal as is less straightforward to interpret). It looks like there are examples of 'principled defense' (citing the target study favourably and providing counter arguments against the replication) and 'hollow defense' (citing the target study favourably but providing no counter arguments against the replication), with a tendency towards the latter.

>>>>

---
title: "PRCP Preliminary Analysis"
output: html_document
---

@@

# Post-replication citation patterns in psychological science: Preliminary analysis

@@

Now we'll plot standardized citation curves and include citations to the set of reference articles. In the graphs below, the annual citation counts for both the target article and reference class are standardized against the calendar year with the highest citation count for the target article (i.e., citations received in that year are set at the standardized value of 100). As defined in the protocol, the reference class in each case is all of the articles published in the same year and in the same journal as the target article. For example, for Baumeister et al. (1998), the reference class is all articles published in 1998 in the Journal of Personality and Social Psychology.

@@

Across all cases, `r d_contentAnalysis %>% count(excluded) %>% filter(excluded == T) %>% pull(n)` citing articles had to be excluded because they could not be accessed (n = `r d_contentAnalysis %>% count(exclusionReason) %>% filter(exclusionReason == "No access") %>% pull(n)`), non-English language (n = `r d_contentAnalysis %>% count(exclusionReason) %>% filter(exclusionReason == "Non-English language") %>% pull(n)`), or because the target article was cited in the references but not in the actual text (n = `r d_contentAnalysis %>% count(exclusionReason) %>% filter(exclusionReason == "Cited in references but not in text") %>% pull(n)`). Excluded articles are represented on the graphs below in light grey.

## Claim correction vs. claim perpetuation.

@@

```{r}
rbind(
  d_summary %>%
  filter(case %in% c('baumeister','strack','sripada'),
         pubYear %in% c(2017,2018,2019)),
  d_summary %>%
    filter(case %in% c('carter', 'caruso'),
           pubYear %in% c(2015,2016,2017,2018,2019))
) %>%
  group_by(case) %>%
  summarise(targetCitations = sum(citesTarget,na.rm=T), 
            replicationCitations = sum(citesRep_yes,na.rm=T)) %>%
  mutate(replicationCitations_percent = round((replicationCitations/targetCitations)*100,0)) %>%
  kable(caption = 'Citations to replication study by articles citing target study in post-replication years') %>%
  kable_styling(full_width = F)
```

@@

## Principled defense vs. hollow defense.

@@

```{r}
rbind(
  d_summary %>%
  filter(case %in% c('baumeister','strack','sripada'),
         pubYear %in% c(2017,2018,2019)),
  d_summary %>%
    filter(case %in% c('carter', 'caruso'),
           pubYear %in% c(2015,2016,2017,2018,2019))
) %>%
  group_by(case) %>%
  summarise(counterargs_yes = sum(counterargs_yes,na.rm=T),
            counterargs_no = sum(counterargs_no,na.rm=T)) %>%
  mutate(counterargs_percent = round(
    (counterargs_yes/(counterargs_yes+counterargs_no))*100,
    0)) %>%
  kable(caption = 'Use of counter arguments when replication study cited') %>%
  kable_styling(full_width = F)
```
